A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Fix wording
Add mu-Calculus intro and definitions

Burch et al.~\cite{BURCH90} and McMillan~\cite{MCMILLAN92} extend Bryant's OBDD
representation~\cite{BRYANT86} by quantification over Boolean variables (QBF) and
substitution of variable names. The quantification over Boolean variables is
realized by using Bryant's \textit{Restrict} operation (see
Section~\ref{sec:operations}). Let $f$ be a QBF formula and $x$ be a Boolean
variable. The QBF formula $\exists x\left(f\right)$ then is equivalent to
$f|_{a=0} \lor f|_{a=1}$~\cite{BURCH90}. Substitution of variables, e.g.
substitute $x$ by $y$ (denoted $f\langle x\leftarrow y\rangle$), is computed using
the following equivalence:
\begin{center}
$
f\langle x\leftarrow y\rangle \equiv
\exists x\lbrack\left(x \Leftrightarrow y\right) \land f\rbrack
$
\end{center}
\tbr

>>>>

Burch et al.~\cite{BURCH90} and McMillan~\cite{MCMILLAN92} extend Bryant's OBDD
representation~\cite{BRYANT86} by quantification over Boolean variables (QBF) and
substitution of variable names. The quantification over Boolean variables is
realized by using Bryant's \textit{Restrict} operation (see
Section~\ref{sec:operations}). Let $f$ be a QBF formula and $x$ be a Boolean
variable. The QBF formula $\exists x\left(f\right)$ then is equivalent to
$f|_{a=0} \lor f|_{a=1}$~\cite{BURCH90}. Substitution of variables, e.g.
substitution of $x$ by $y$ (denoted $f\langle x\leftarrow y\rangle$), is computed
using the following equivalence:
\begin{center}
$
f\langle x\leftarrow y\rangle \equiv
\exists x\lbrack\left(x \Leftrightarrow y\right) \land f\rbrack
$
\end{center}

Before discussing the symbolic model checking algorithms \texttt{BDD}$_f$ and
\texttt{BDD}$_R$, the used $\mu$-Calculus has to be described. For a given finite
signature $\mathcal{S}$, each symbol is either an individual or a predicate
variable having positive arity. Burch et al.~\cite{BURCH90} considered two
syntactic categories, i.e. \textit{formulas} and \textit{relational terms}, having
the following forms.

\noindent
\textbf{Formulas:}~\cite{BURCH90}
\begin{enumerate}
    \item{\textbf{True}, \textbf{False}}.
    \item{
        $\lbrack z_1 = z_2 \rbrack$; $z_{1, 2}\in\mathcal{S}$ are individual
        variables.
    }
    \item{
        $\neg f$, $f \lor g$, $\exists z\left( f \right)$; $z\in\mathcal{S}$ is
        an individual variable, $f$ and $g$ are formulas.
    }
    \item{
        $P\left(z_1, \ldots, z_n\right)$; $P$ is an $n$-ary relational term and
        \newline $z_{1, \ldots, n}\in\mathcal{S}$ are individual variables not
        free in $P$.
    }
\end{enumerate}
\textbf{$n$-ary relational terms:}~\cite{BURCH90}
\begin{enumerate}
    \item{$Z$; $Z\in\mathcal{S}$ is an $n$-ary predicate variable.}
    \item{
        $\lambda z_1, \ldots, z_n\left( f \right)$; $f$ is a formula and
        $z_1, \ldots, z_n\in\mathcal{S}$ are distinct individual variables.
    }
    \item{
        $\mu Z \left( P \right)$; $Z\in\mathcal{S}$ is an $n$-ary predicate variable
        and $P$ is an $n$-ary relational term \textit{formally monotone in} $Z$,
        i.e. all free occurrences of $Z$ in $P$ have to be evenly negated. This
        $n$-ary relatioinal term is the \textit{least fixed point} (\textit{lfp})
        of an $n$-ary relational term $P$. Analogous, $\nu Z \left( P \right)$ is
        the \textit{greatest fixed point} (\textit{gfp}) and is equivalent to
        $\neg\mu Z \left( \neg P \langle Z \leftarrow \left( \neg Z \right) \rangle \right)$.
    }
\end{enumerate}

\tbr
